### 2022-09-15 chapters/benchmarking/draft.tex

\subsection{Docker Vs. Virtual Machine}
Despite the fact that Type 1 is more performant than Type 2, the latter is the most used in research, as most researchers tend to conduct their experiments on their own machines. Docker, on the other hand, is the most well-known container technology. In our case, we are more likely to promote Docker for two reasons:
\begin{enumerate}
    \item As previously stated [143] [reference Morabito (2015) and van Kessel et al. (2016)], we require a lightweight orchestrator to limit the overhead on energy usage of our experiments
          \cite{van2016power}
          % TODO : ask romain about the title of the paper and the reference to the paper
          [cite Morabito (2015) and van Kessel et al. (2016)],
          % cite Power efficiency of hypervisor-based virtuali- zation versus container-based virtualization. University of Amsterdam.
    \item We need to communicate with the host OS because we are using hardware sensors to measure the energy consumption.
\end{enumerate}

%  TODO : Rephrase this 
% A special notice to \href{https://github.com/powerapi-ng/virtualwatts}{virtualwatts}. A framework that enables us to retrieve the energy consumption of a virtual machine.

>>>>

\subsection{Docker Vs. Virtual Machine}
Despite the fact that Type 1 is more performant than Type 2, the latter is the most used in research, as most researchers tend to conduct their experiments on their own machines. Docker, on the other hand, is the most well-known container technology. In our case, we are more likely to promote Docker for two reasons:
\begin{enumerate}
    \item As previously stated in literature~\cite{van2016power,morabito_power_2015}, we require a lightweight orchestrator to limit the overhead on energy usage of our experiments
    \item We need to communicate with the host OS because we are using hardware sensors to measure the energy consumption.
\end{enumerate}

% A special notice to \href{https://github.com/powerapi-ng/virtualwatts}{virtualwatts}. A framework that enables us to retrieve the energy consumption of a virtual machine.
